Continuous Generalization of Buildings by Growing and Merging

### 2017-09-03 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
move to the format of ACM Sigspatial

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a contributed volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}
\usepackage{etex}

\newcommand{\blndraft}{true}
%\newcommand{\blndraft}{false}

%\usepackage[english]{babel}
%
\usepackage[utf8]{inputenc}
% choose options for [] as required from the list
% in the Reference Guide

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
%\usepackage[]{graphicx}
\usepackage[draft]{graphicx}        % standard LaTeX graphics tool
\usepackage[size=small,labelfont=bf]{caption}
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
\usepackage{pdflscape}
%\usepackage{rotating}
\usepackage{afterpage}
%\usepackage[disable]{todonotes}
\usepackage[colorinlistoftodos,prependcaption]{todonotes}
%\usepackage{todonotes}
\usepackage{subfigure}
\usepackage{setspace}
\usepackage{epstopdf}
\usepackage{flafter} %make sure that the floats are not placed 
%before their definition
\usepackage{times}
\usepackage{bm}
\usepackage{gensymb}  % for degree sign, e.g., temperature
\usepackage{amsmath}
\usepackage{amstext}
\usepackage{array}  %for define the fomats of columns in a table
\usepackage{dcolumn}
\usepackage[T1]{fontenc}
\usepackage{pgfplots}
\usepackage{multirow}
\usepackage{makecell}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage{capt-of}
%\usepackage{marginnote}
\usepackage{xargs}   % Use more than one 
%optional parameter in a new commands
%\usepackage{siunitx} %for scientific 
%notation
%%we do this because of a bug of package floatrow
%\let\tmp\newinsert
%\let\newinsert\newbox
%\usepackage{floatrow}
%\let\newinsert\tmp
\usepackage{enumitem} %make items indent when using 
%\begin{enumerate}[(a)]
\usepackage{verbatimbox}  %for \addvbuffer
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{xspace}
%\usepackage{pdfcomment}
%\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=1pt] (char) {#1};}}
%\newcommand*\circledtwo[1]{\tikz[baseline=(char.base)]{
%		\node[shape=circle,draw,inner sep=0.1pt] (char) {#1};}}
\newcommand{\maps}{\ensuremath{M_\mathrm{s}}\xspace}
\newcommand{\mapg}{\ensuremath{M_\mathrm{g}}\xspace}

\usepackage[backend=bibtex,
bibstyle=authoryear, %without indices before names; year after 
%names
%style=authoryear,
citestyle=authoryear,
maxbibnames=20,maxcitenames=2,
firstinits=true,
%terseinits=true, %remove periods after initials of first names
%style=apa, %
%sorting=ydnt, %Sort bibliography by year (descending), name, 
%title
doi=false,isbn=false,url=false,
eprint=false,dashed=false]{biblatex}

%\renewcommand*{\bibfont}{\small} %set the font size of the 
%references
%\renewcommand*{\nameyeardelim}{\addspace} %\remove the comma 
%between author and year citations
%\renewcommand*{\revsdnamepunct}{} %remove commas between last 
%%and first names in bibliography
%\renewcommand{\labelnamepunct}{\addspace} %remove the 
%%punctuation after the year in bibliography
%\renewcommand{\finentrypunct}{} %remove the full stop at the 
%%end of each bibliography entry
\renewcommand*{\revsdnamepunct}{} %remove commas between last 
%and first names in bibliography

%remove "In:" for articles in bibliography
\renewbibmacro{in:}{\ifentrytype{article}{}
	{\printtext{\bibstring{in}\intitlepunct}}}

\addbibresource{References.bib}

\newcommand{\mypar}[1]{\bigskip\noindent\textbf{#1.}~}

\newcommand{\e}[1]{\times 10^{#1}}
\newcommand{\fig}{Fig.~}
\newcommand{\eq}{Eq.~}
\newcommand{\sect}{Sec.~}
\newcommand{\tab}{Tab.~}
\newcommand{\figs}{Figs.~}
\newcommand{\eqs}{Eqs.~}
\newcommand{\sects}{Secs.~}
\newcommand{\tabs}{Tabs.~}

%\newcommand{\myeqref}[1]{Eq.~\ref{#1}}
%\newcommand{\mysectref}[1]{Sec.~\ref{#1}}
%\newcommand{\myfigref}[1]{Fig.~\ref{#1}}
%\newcommand{\mytabref}[1]{Tab.~\ref{#1}}

\newcommand{\dtrm}[2][]{d_{\mathrm{#2}, t\ifthenelse{\equal{#1}{}}{}{_#1}}}

\graphicspath{{figures/}}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}

%For the references, the following commands make the titles 
%lowercase while keep the initial letters of journal names 
%uppercase
\DeclareFieldFormat{titlecase}{\MakeSentenceCase*{#1}}
\newbibmacro*{journal}{%
	\iffieldundef{journaltitle}
	{}
	{\printtext[journaltitle]{%
			\printfield[myplain]{journaltitle}%
			\setunit{\subtitlepunct}%
			\printfield[myplain]{journalsubtitle}}}}
\DeclareFieldFormat{myplain}{#1}

%Remove the quotation marks for the titles in the reference
\DeclareFieldFormat[article,inbook,incollection,inproceedings,patent,thesis,unpublished]{citetitle}{#1}
\DeclareFieldFormat[article,inbook,incollection,inproceedings,patent,thesis,unpublished]{title}{#1}
\DeclareNameAlias{author}{last-first}

%%Using \DeclarePairedDelimiter from mathtools, you could define 
%%macros \ceil and \floor, which will scale the delimiters 
%%properly (if starred):
%\usepackage{mathtools}
%\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
%\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\pgfplotsset{
	compat=newest,
	xlabel near ticks,
	ylabel near ticks
}

\newcommandx{\marginalcomment}[2][1=]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue,#1]{#2}}

\renewcommand{\textfraction}{0.01}
\renewcommand{\topfraction}{0.99}
\renewcommand{\bottomfraction}{0.99}
\renewcommand{\dbltopfraction}{0.99} % fit big float above 
%2-col. text
%\renewcommand\thesection{\arabic{section}}
%\renewcommand\thesubsection{\thesection.\arabic{subsection}}

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title*{Continuous Generalization of Buildings \protect\\ by Growing and 
Merging}
\titlerunning{Continuous Generalization of Buildings}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Dongliang Peng and Guillaume Touya}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{
	Dongliang Peng 
	\at Chair of Computer Science I, University of W\"urzburg, 
	Germany \\
	\email{dongliang.peng@uni-wuerzburg.de}
	\and
	% 
	Guillaume Touya
	\at COGIT, IGN, France \\
	\email{guillaume.touya@ign.fr}
}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\newcommand{\myabstract}{We propose a method to continuously 
	generalize buildings from a given start scale to a smaller goal scale. 
	%
	If several buildings are close to each other at the start 
	scale, we bridge them by line segments and merge the several buildings into 
	one 
	building.
	For each building, either an original one or a merged one, at the start 
	scale, 
	we generate its target shape at 
	the goal scale by enlarging and simplifying. 
	Then we grow the building to the target shape.
	%
	After finishing the growing, we can take the goal scale as the 
	start scale and repeat the process.
	\newline\indent
	The advantages of our method are as follows. First, the buildings 
	are enlarged continuously. At the same time, they are simplified. 
	Second, we ensure that the distance between any pair of two buildings is 
	always larger than a specified threshold.}

\abstract*{\myabstract}

\abstract{\myabstract}

\keywords{Text, Text}

@@

Digital maps such as Google Maps and OpenStreetMap support zooming by 
displaying maps at different levels. 
This discrete strategy may results in sudden changes, which annoy users.
To provide better zooming experience, continuous generalization aims to 
produce 
a sequence of maps with small incremental changes.
To realize continuous generalization, \textcite{Sester2005_CG} discussed some 
generalization operators for buildings and proposed to morph a building 
between 
its forms at different levels. Morphing has been used to generate intermediate 
representations for two representations at different scales 
\parencite{mnwb-mpstc-08,Peng2013_LSA,Deng2015,Peng2016_Admin}. 
Also aiming at 
realize continuous generalization, \textcite{Chimani2014_Eat} generated a good 
selection sequence for road networks, and 
\textcite{Peng2017_AStar} tried to compute optimal aggregation sequences for 
land-cover areas.

When users zoom out on digital maps, buildings become closer with each other 
and buildings themselves become smaller. 
In order to make sure that the map is 
easily perceived \parencite{Weibel1997}, small building should be eliminated, 
some building should be enlarged, and buildings close to each other should be 
aggregated.
Although algorithms of simplifying buildings have been studied, e.g., 
\textcite{Buchin2011_Simp,haunertwolff2010}, problems become more complicated 
when we have to aggregate buildings simultaneously.
In order to aggregate, we should first group the buildings.

@@

The papers we may review:   
\textcite{vanSmaalen2003, Buchin2016, Chaudhry2008, Stoter2009},

Rules for building simplification; see \textcite{Lee2005}

Straight skeletons for map generalization: 
\textcite{Gold2003,Matuk2006}

An example of enlargement in aggregation: \citetitle{Neun2005}

Using MST to group buildings: \textcite{Zhang2013, 
Cetinkaya2015,Deng2017,Regnauld1996}

@@

\todo[inline]{a brief introduction of our method.}
We name our input map as start map,
and denote the scale of the start map by $1:M_\mathrm{s}$.
We generate a goal map \mapg at scale $1:M_\mathrm{g}$ 
($M_\mathrm{g} > M_\mathrm{s}$) by generalizing the start map. 
We use time $t\in[0,1]$ to define the continuous generalization
process. 
We require that the generalization yields exactly the start map when $t=0$, 
the goal map when $t=1$, 
and that the start map is continuously generalized into the goal map 
when $t$ increases from~$0$ to~$1$.
For the sake of convenience, we define parameter
$M_t= M_\mathrm{s} + t \cdot (M_\mathrm{g}-M_\mathrm{s})$.

@@

\begin{figure}[tb]
	\centering
	\includegraphics{Buffer_MiterLimits}
	\caption{}
	\label{fig:Buffer_MiterLimits}
\end{figure}

@@

\begin{figure}[tb]
	\centering
	\includegraphics{Growth}
	\caption{Growth.}
	\label{fig:Growth}
\end{figure}

\subsection{Simplify grown buildings}
\label{sec:Simplify}
We use a buffering-based method, 
similar to \textcite{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes
(see \fig\ref{fig:RemovePitAndSpike}).

\begin{figure}[tb]
	\centering
	\includegraphics[]{RemovePitAndSpike}
	\caption{Remove a pit by dilating and then remove a spike by eroding.
		(a) a polygon with a pit and a spike;
		(b) dilate the polygon in (a) with distance $d$ to remove the pit;
		(c) erode the polygon in (b) with distance $2d$ to remove the spike;
		(d) dilate the polygon in (c) with distance $d$ so that the result has 
		the same size as the polygon in (a).
	}
	\label{fig:RemovePitAndSpike}
\end{figure}

@@

We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$
(see \eq\ref{eq:d_epsilont}) so that
any pits and spikes narrower than $l$ will be removed. 
We set $l=0.3\,\mathrm{mm}$, which was used as a length threshold by 
\textcite{Regnauld2001,Li2004,Basaraner2008}.
According to \eq\ref{eq:d_Gt}, $\dtrm{G}$ can be arbitrarily small 
when $t$ is small, 
but $d_{\epsilon, t}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
As a compromise, we use
\begin{equation}
\label{eq:d_Et}
\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
\end{equation}
Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
t \cdot \frac{l}{2} M_\mathrm{g} >0$.
As a result, we should make sure that
\begin{equation}
\label{eq:S_g}
M_\mathrm{g} > \frac{\lambda\sqrt{a}}{\lambda\sqrt{a}-l} S_s.
\end{equation}

@@

After carrying out the buffering-based methods, 
we simplify the grown buildings using Imai--Iri algorithm 
\parencite{ImaiIri1988}.
This algorithm first finds all the valid shortcuts of a polyline.
A shortcut is valid for a segment 
if the distance between the segment and the shortcut is at most a specified 
value
(see \fig\ref{fig:ImaiIri_Shortcut}).
We set the value also as $l$.
That is, at time $t$, the threshold distance is
\begin{equation}
\label{eq:d_lt}
d_{l,t}= l \cdot M_t.
\end{equation}
Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
of a polyline to the end, using breadth-first search.
The sequence of valid shortcuts is an approximation of the polyline, 
and has the least number of line segments.

@@

We tried simplifying using 
the Douglas--Peucker algorithm \parencite{Douglas1973}, 
but we hoped to remove more points. 
We found that the Imai--Iri 
algorithm fit our needs better.

@@

\begin{figure}[tb]
	\centering
	\includegraphics[]{Shrink_Erosion}
	\caption{A building shrinks during growing because of dilation and erosion, 
	where $t_1=0.6$, $t_2=0.7$, and $t_3=1$.
		The small gray polygons represent the original building.
		(a) Grow and Dilate the building with distances $\dtrm[1]{G}$ and 
		$\dtrm[1]{D}$, respectively;
		(b) Erode the polygon in (a) with distance $\dtrm[1]{D} + \dtrm[1]{E}$;
		(c) Dilate the polygon in (b) with distance $\dtrm[1]{E}$.
		(d) The large gray polygon is the target shape on goal map.
		The process for (e), (f), and (g) is the same as the process of (a), 
		(b), and (c).
		The darker gray piece in (g) shows 
		the part which is included in the grown polygon of (c), 
		but not in the grown polygon of (g).
	}
	\label{fig:Shrink_Erosion}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[]{Shrink_Simplification}
	\caption{A building shrinks during growing because of line simplification, 
		where $t_1=0.7$, $t_2=0.8$, and $t_3=1$.
		The small gray polygons represent the original building.
		The process for (a), (b), and (c), and 
		the process for (e), (f), and (g) are the same as 
		the processes in \fig\ref{fig:Shrink_Erosion}.
		(d) The large gray polygon is the target shape on goal map.
		(h) Simplify the polygon in (g) using the Imai--Iri algorithm.
		Note that $d_{l,t_1}<d_{l,t_2}$ see \eq\ref{eq:d_lt}),
		which is why the Imai--Iri algorithm does not 
		remove any point of the polygon in (c),
		but removes two points of the polygon in (g).
		The darker gray pieces in (h) show 
		the parts which are included in the polygon of (c), 
		but not in the polygon of (h).
	}
	\label{fig:Shrink_Simplification}
\end{figure}

@@

\subsection{Merge close buildings by introducing bridges}
The distance between two buildings on a map should be larger than a threshold
\parencite{Regnauld2001,Li2004}.
Following \textcite{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
The real separation distance at time $t$ is
\begin{equation}
	\label{eq:d_epsilont}
	d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

@@

\begin{figure}[tb]
	\centering
	\includegraphics[draft=false]{GrowAndBridge}
	\caption{Merge buildings by introducing bridges when the buildings become 
		too close.
		Although the bridges appear at different time, 
		their widths are the same (see the figure with $t=1$).}
	\label{fig:GrowAndBridge}
\end{figure}

For each pair of buildings in the same group, 
we find the smallest distance between them.
We connect the buildings by adding an edge from the nearest points.
We find a minimum spanning tree of the buildings using Prim's algorithm 
\parencite{Prim1957}.
We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.

\subsection{Group buildings based on buffering}
\label{sec:Grouping}
We group buildings based on the buffers of the buildings. 
We buffer each building with distance $d_G + \frac{d_\epsilon}{2}$, 
where distance $d_G$ is the growing amount of each building. 
Parameter $d_\epsilon$ is the least distance allowed between two buildings.
We grow an additional $\frac{d_\epsilon}{2}$ so that if two buffers overlap, 
the corresponding two buildings will become too close during our growing step.
The two buildings are identified as in the same group.

@@

If we insist on that we should observe 
the growing, say, $x \% (0<x<100)$ of the time at least, then we should make 
sure that
\begin{equation}
\label{eq:a_limit}
\frac{d_\mathrm{G}}{d_\mathrm{G}+d_\epsilon} \ge x \%.
\end{equation}
Using $d_\mathrm{G}$ and $d_\epsilon$ from Eqs.~\ref{eq:d_G} 
and~\ref{eq:d_epsilon}, we transform Eq.~\ref{eq:a_limit} to
\begin{equation}
a \ge \Big(\frac{2 \epsilon S_g x}{\lambda (100-x) (S_g-S_s)}\Big)^2
\end{equation}
We also require 
that $S_g \ge 2 S_s$, which means $S_s \le \frac{1}{2} S_g$.
On one hand, we should have a large $x$ so that we will see the 
growing most of the time.
On the other hand, we wish to keep bridges short as bridges are intrusions to 
our map, which means we should have a small $x$ and a large $\lambda$ so that 
we will have a small 
$a$ (according to Eq.~\ref{eq:a_limit}), a small $d_\mathrm{G}$ (according to 
Eq.~\ref{eq:d_G}), and finally a small $l_b$ (according to 
Eq.~\ref{eq:BridgeLength}). Also we should have a small $x$ and a large 
$\lambda$ as our $a$ is already much larger than $0.16\,\mathrm{mm}^2$ on 
map, which is the area limit used by \textcite{Stoter2009}. As a result, we 
set 
$\lambda=0.8$ and $x=\frac{2}{3} \cdot 100$.
Using these setting, we have
\begin{equation}
a \ge 4.
\end{equation}
according to Eq.~\ref{eq:a_limit}.

@@

\textcite{Chaudhry2008} thought that a hole of a settlement should be at least 
$0.5\,\mathrm{km}^2$ for a map at scale $1:250{,}000$, 
which means that the hole is at least $8\,\mathrm{mm}^2$ on map. 
Following their setting, we shrink a hole and 
eliminate the hole once its size is smaller than $8\,\mathrm{mm}^2$ on map.

%
%A hole has area less than $\pi D_\mathrm{G}^2$ can be filled by growing. 
%A hole has area 
%slightly more than $\pi D_\mathrm{G}^2$ will become a very small hole after 
%growing with 
%distance $D_\mathrm{G}$. In order to avoid small holes, we do not fill a hole 
%unless the 
%area of the hole on the start map is smaller than $\pi D_\mathrm{G}^2$. Note 
%that we do 
%not fill a hole even if the hole has a large area because a large hole may be 
%split into several small holes by filling. 
%Although our intermediate results may violate the rule that a hole should be 
%at 
%least some size, we try to avoid the violation for a map at a goal scale.
%\textcite{Chaudhry2008} thought that a hole of a settlement should be at 
%least 
%$0.5$ km$^2$ for a map at scale $1:250{,}000$, which means that the hole is 
%at 
%least $8\,\mathrm{mm}^2$ on the map. Following their setting, we wish to have 
%$\pi 
%D_\mathrm{G}^2 \ge 8 S_g^2$.
%
%
%Now we discuss how to set the parameters according to our requirements. 
%First, 
%we wish to increase $d_\mathrm{G}/d_\epsilon$. Most part of a building will 
%grow $d_\mathrm{G}$. Only a small part will continue growing after the 
%building 
%has grown $d_\mathrm{G}$. To ensure that we can see the growing most of the 
%time, we want to have a large $d_\mathrm{G}/d_\epsilon$.
%
%
%
%
%
%We cannot fulfill all the requirements.

\begin{figure}[tb]
	\centering
	\includegraphics{ExtraGrowth}
	\caption{In the left figure, the green polygon represents a building, and 
	the gray polygon is the enlargement of the building. In the right 
	figure, the gray polygon has been simplified to a rectangle. In order to 
	fill the rectangle, most parts of the (green) building needs to grow with
	distance $d_\mathrm{G}$, but the pit needs to grow with $d_G + 
	d_\mathrm{e}$, 
	where $d_\mathrm{e}$ is the extra growing distance.}
	\label{fig:ExtraGrowth}
\end{figure}

>>>>

@@

Digital maps such as Google Maps and OpenStreetMap support zooming by 
displaying maps at different levels. 
This discrete strategy may results in sudden changes, which annoy users.
To provide better zooming experience, continuous generalization aims to 
produce 
a sequence of maps with small incremental changes.
To realize continuous generalization, \citet{Sester2005_CG} discussed some 
generalization operators for buildings and proposed to morph a building 
between 
its forms at different levels. 
Morphing has been used to generate intermediate 
representations for two representations at different scales 
\citep{mnwb-mpstc-08,Peng2013_LSA,Deng2015,Peng2016_Admin}. 
Also aiming at 
realize continuous generalization, \citet{Chimani2014_Eat} generated a good 
selection sequence for road networks, and 
\citet{Peng2017_AStar} tried to compute optimal aggregation sequences for 
land-cover areas.

When users zoom out on digital maps, buildings become closer with each other 
and buildings themselves become smaller. 
In order to make sure that the map is 
easily perceived \citep{Weibel1997}, small building should be eliminated, 
some building should be enlarged, and buildings close to each other should be 
aggregated.
Although algorithms of simplifying buildings have been studied, e.g., 
\citet{Buchin2011_Simp,haunertwolff2010}, problems become more complicated 
when we have to aggregate buildings simultaneously.
In order to aggregate, we should first group the buildings.

@@

The papers we may review:   
\citet{vanSmaalen2003, Buchin2016, Chaudhry2008, Stoter2009},

Rules for building simplification; see \citet{Lee2005}

Straight skeletons for map generalization: 
\citet{Gold2003,Matuk2006}

An example of enlargement in aggregation: \citet{Neun2005}

Using MST to group buildings: \citet{Zhang2013, 
	Cetinkaya2015,Deng2017,Regnauld1996}

@@

\todo[inline]{a brief introduction of our method.}
We name our input map as start map,
and denote the scale of the start map by $1:M_\mathrm{s}$.
We generate a goal map at scale $1:M_\mathrm{g}$ 
($M_\mathrm{g} > M_\mathrm{s}$) by generalizing the start map. 
We use time $t\in[0,1]$ to define the continuous generalization
process. 
We require that the generalization yields exactly the start map when $t=0$, 
the goal map when $t=1$, 
and that the start map is continuously generalized into the goal map 
when $t$ increases from~$0$ to~$1$.
For the sake of convenience, we define parameter
$M_t= M_\mathrm{s} + t \cdot (M_\mathrm{g}-M_\mathrm{s})$.

@@

\begin{figure*}[tb]
	\centering
	\includegraphics{Buffer_MiterLimits}
	\caption{}
	\label{fig:Buffer_MiterLimits}
\end{figure*}

@@

\begin{figure*}[tb]
	\centering
	\includegraphics{Growth}
	\caption{Growth.}
	\label{fig:Growth}
\end{figure*}

\subsection{Simplify grown buildings}
\label{sec:Simplify}
We use a buffering-based method, 
similar to \citet{Damen2008,Meijers2016}, 
to simplify our grown buildings. 
We first dilate the grown buildings to remove 
pits, and then erode the results to remove spikes
(see \fig\ref{fig:RemovePitAndSpike}).

\begin{figure*}[tb]
	\centering
	\includegraphics[]{RemovePitAndSpike}
	\caption{Remove a pit by dilating and then remove a spike by eroding.
		(a) a polygon with a pit and a spike;
		(b) dilate the polygon in (a) with distance $d$ to remove the pit;
		(c) erode the polygon in (b) with distance $2d$ to remove the spike;
		(d) dilate the polygon in (c) with distance $d$ so that the result has 
		the same size as the polygon in (a).
	}
	\label{fig:RemovePitAndSpike}
\end{figure*}

@@

We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$
(see \eq\ref{eq:d_epsilont}) so that
any pits and spikes narrower than $l$ will be removed. 
We set $l=0.3\,\mathrm{mm}$, which was used as a length threshold by 
\citet{Regnauld2001,Li2004,Basaraner2008}.
Distance $\dtrm{G}$ can be arbitrarily small according to \eq\ref{eq:d_Gt}, 
but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
As a compromise, we use
\begin{equation}
\label{eq:d_Et}
\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
\end{equation}
Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
t \cdot \frac{l}{2} M_\mathrm{g} >0$.
As a result, we should make sure that
\begin{equation}
\label{eq:S_g}
M_\mathrm{g} > \frac{\lambda\sqrt{a}}{\lambda\sqrt{a}-l} S_s.
\end{equation}

@@

After carrying out the buffering-based methods, 
we simplify the grown buildings using Imai--Iri algorithm 
\citep{ImaiIri1988}.
This algorithm first finds all the valid shortcuts of a polyline.
A shortcut is valid for a segment 
if the distance between the segment and the shortcut is at most a specified 
value
(see \fig\ref{fig:ImaiIri_Shortcut}).
We set the value also as $l$.
That is, at time $t$, the threshold distance is
\begin{equation}
\label{eq:d_lt}
d_{l,t}= l \cdot M_t.
\end{equation}
Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
of a polyline to the end, using breadth-first search.
The sequence of valid shortcuts is an approximation of the polyline, 
and has the least number of line segments.

@@

We tried simplifying using 
the Douglas--Peucker algorithm \citep{Douglas1973}, 
but we hoped to remove more points. 
We found that the Imai--Iri 
algorithm fit our needs better.

@@

\begin{figure*}[tb]
	\centering
	\includegraphics[]{Shrink_Erosion}
	\caption{A building shrinks during growing because of dilation and erosion, 
		where $t_1=0.6$, $t_2=0.7$, and $t_3=1$.
		The small gray polygons represent the original building.
		(a) Grow and Dilate the building with distances $\dtrm[1]{G}$ and 
		$\dtrm[1]{D}$, respectively;
		(b) Erode the polygon in (a) with distance $\dtrm[1]{D} + \dtrm[1]{E}$;
		(c) Dilate the polygon in (b) with distance $\dtrm[1]{E}$.
		(d) The large gray polygon is the target shape on goal map.
		The process for (e), (f), and (g) is the same as the process of (a), 
		(b), and (c).
		The darker gray piece in (g) shows 
		the part which is included in the grown polygon of (c), 
		but not in the grown polygon of (g).
	}
	\label{fig:Shrink_Erosion}
\end{figure*}

\begin{figure*}[tb]
	\centering
	\includegraphics[]{Shrink_Simplification}
	\caption{A building shrinks during growing because of line simplification, 
		where $t_1=0.7$, $t_2=0.8$, and $t_3=1$.
		The small gray polygons represent the original building.
		The process for (a), (b), and (c), and 
		the process for (e), (f), and (g) are the same as 
		the processes in \fig\ref{fig:Shrink_Erosion}.
		(d) The large gray polygon is the target shape on goal map.
		(h) Simplify the polygon in (g) using the Imai--Iri algorithm.
		Note that $d_{l,t_1}<d_{l,t_2}$ see \eq\ref{eq:d_lt}),
		which is why the Imai--Iri algorithm does not 
		remove any point of the polygon in (c),
		but removes two points of the polygon in (g).
		The darker gray pieces in (h) show 
		the parts which are included in the polygon of (c), 
		but not in the polygon of (h).
	}
	\label{fig:Shrink_Simplification}
\end{figure*}

@@

\subsection{Merge close buildings by introducing bridges}
The distance between two buildings on a map should be larger than a threshold
\citep{Regnauld2001,Li2004}.
Following \citet{Basaraner2008,Stoter2009}, 
we set the separation threshold $\epsilon= 0.2\,\mathrm{mm}$. 
The real separation distance at time $t$ is
\begin{equation}
\label{eq:d_epsilont}
d_{\epsilon, t} = \epsilon \cdot M_t.
\end{equation}

@@

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{GrowAndBridge}
	\caption{Merge buildings by introducing bridges when the buildings become 
		too close.
		Although the bridges appear at different time, 
		their widths are the same (see the figure with $t=1$).}
	\label{fig:GrowAndBridge}
\end{figure*}

For each pair of buildings in the same group, 
we find the smallest distance between them.
We connect the buildings by adding an edge from the nearest points.
We find a minimum spanning tree of the buildings using Prim's algorithm 
\citep{Prim1957}.
We enlarge and merge buildings as the way we do in \sect\ref{sec:Grouping}.

\subsection{Group buildings based on buffering}
\label{sec:Grouping}
We group buildings based on the buffers of the buildings. 
We buffer each building with distance $\dtrm{G} + d_{\epsilon,t}/2$
(see \eqs\ref{eq:d_Gt} and~\ref{eq:d_epsilont}).
We grow an additional $d_{\epsilon,t}/2$ so that if two buffers overlap, 
the corresponding two buildings will become too close at time $t$.
As a result, the two buildings are identified as in the same group.

@@

If we insist on that we should observe 
the growing, say, $x \% (0<x<100)$ of the time at least, then we should make 
sure that
\begin{equation}
\label{eq:a_limit}
\frac{d_\mathrm{G}}{d_\mathrm{G}+d_\epsilon} \ge x \%.
\end{equation}
Using $d_\mathrm{G}$ and $d_\epsilon$ from Eqs.~\ref{eq:d_G} 
and~\ref{eq:d_epsilon}, we transform Eq.~\ref{eq:a_limit} to
\begin{equation}
a \ge \Big(\frac{2 \epsilon S_g x}{\lambda (100-x) (S_g-S_s)}\Big)^2
\end{equation}
We also require 
that $S_g \ge 2 S_s$, which means $S_s \le \frac{1}{2} S_g$.
On one hand, we should have a large $x$ so that we will see the 
growing most of the time.
On the other hand, we wish to keep bridges short as bridges are intrusions to 
our map, which means we should have a small $x$ and a large $\lambda$ so that 
we will have a small 
$a$ (according to Eq.~\ref{eq:a_limit}), a small $d_\mathrm{G}$ (according to 
Eq.~\ref{eq:d_G}), and finally a small $l_b$ (according to 
Eq.~\ref{eq:BridgeLength}). Also we should have a small $x$ and a large 
$\lambda$ as our $a$ is already much larger than $0.16\,\mathrm{mm}^2$ on 
map, which is the area limit used by \citet{Stoter2009}. As a result, we 
set 
$\lambda=0.8$ and $x=\frac{2}{3} \cdot 100$.
Using these setting, we have
\begin{equation}
a \ge 4.
\end{equation}
according to Eq.~\ref{eq:a_limit}.

@@

\citet{Chaudhry2008} thought that a hole of a settlement should be at least 
$0.5\,\mathrm{km}^2$ for a map at scale $1:250{,}000$, 
which means that the hole is at least $8\,\mathrm{mm}^2$ on map. 
Following their setting, we shrink a hole and 
eliminate the hole once its size is smaller than $8\,\mathrm{mm}^2$ on map.

%
%A hole has area less than $\pi D_\mathrm{G}^2$ can be filled by growing. 
%A hole has area 
%slightly more than $\pi D_\mathrm{G}^2$ will become a very small hole after 
%growing with 
%distance $D_\mathrm{G}$. In order to avoid small holes, we do not fill a hole 
%unless the 
%area of the hole on the start map is smaller than $\pi D_\mathrm{G}^2$. Note 
%that we do 
%not fill a hole even if the hole has a large area because a large hole may be 
%split into several small holes by filling. 
%Although our intermediate results may violate the rule that a hole should be 
%at 
%least some size, we try to avoid the violation for a map at a goal scale.
%\citet{Chaudhry2008} thought that a hole of a settlement should be at 
%least 
%$0.5$ km$^2$ for a map at scale $1:250{,}000$, which means that the hole is 
%at 
%least $8\,\mathrm{mm}^2$ on the map. Following their setting, we wish to have 
%$\pi 
%D_\mathrm{G}^2 \ge 8 S_g^2$.
%
%
%Now we discuss how to set the parameters according to our requirements. 
%First, 
%we wish to increase $d_\mathrm{G}/d_\epsilon$. Most part of a building will 
%grow $d_\mathrm{G}$. Only a small part will continue growing after the 
%building 
%has grown $d_\mathrm{G}$. To ensure that we can see the growing most of the 
%time, we want to have a large $d_\mathrm{G}/d_\epsilon$.
%
%
%
%
%
%We cannot fulfill all the requirements.

\begin{figure*}[tb]
	\centering
	\includegraphics{ExtraGrowth}
	\caption{In the left figure, the green polygon represents a building, and 
		the gray polygon is the enlargement of the building. In the right 
		figure, the gray polygon has been simplified to a rectangle. In order 
to 
		fill the rectangle, most parts of the (green) building needs to grow 
with
		distance $d_\mathrm{G}$, but the pit needs to grow with $d_G + 
		d_\mathrm{e}$, 
		where $d_\mathrm{e}$ is the extra growing distance.}
	\label{fig:ExtraGrowth}
\end{figure*}
